Arbeidskrav våren 2022

### 2022-01-13 MSB106_Arbeidskrav_V22_Backup.Rmd
Nytt forsøk

LQindustri <- syssel_bos %>% 
  select(aar, knavn, Eir_Er_industri) %>% 
  mutate(aar = as.character(aar)) %>% 
  left_join(select(.data = nasjonalt_bosted, aar, Ein_En_Industri), by = c("aar")) %>% 
  mutate(
  andel = Eir_Er_industri/Ein_En_Industri
  )

>>>>

LQindustri <- syssel_bos %>% 
  select(aar, knavn, Eir_Er_industri) %>% 
  mutate(aar = as.character(aar)) %>% 
  left_join(select(.data = nasjonalt_bosted, aar, Ein_En_Industri), by = c("aar")) %>% 
  mutate(
  andel = Eir_Er_industri/Ein_En_Industri
  )
# Disse må fikses på tilsvarende vis. Har feil verdier slik de er nå

# LQjordbruk <- as_tibble(syssel_bos$Eir_Er_Jordbruk/nasjonalt_bosted$Ein_En_Jordbruk)

LQjordbruk <- syssel_bos %>% 
  select(aar, knavn, Eir_Er_Jordbruk) %>% 
  mutate(aar = as.character(aar)) %>% 
  left_join(select(.data = nasjonalt_bosted, aar, Ein_En_Jordbruk), by = c("aar")) %>% 
  mutate(andel = Eir_Er_Jordbruk/Ein_En_Jordbruk)

# LQundervisning <- as_tibble(syssel_bos$Eir_Er_Undervisning/nasjonalt_bosted$Ein_En_Undervisning)

LQundervisning <- syssel_bos %>% 
  select(aar, knavn, Eir_Er_Undervisning) %>% 
  mutate(aar = as.character(aar)) %>% 
  left_join(select(.data = nasjonalt_bosted, aar, Ein_En_Undervisning), by = c("aar")) %>% 
  mutate(andel = Eir_Er_Undervisning/Ein_En_Undervisning)

# LQhelse <- as_tibble(syssel_bos$Eir_Er_Helse/nasjonalt_bosted$Ein_En_Helse)

LQhelse <- syssel_bos %>% 
  select(aar, knavn, Eir_Er_Helse) %>% 
  mutate(aar = as.character(aar)) %>% 
  left_join(select(.data = nasjonalt_bosted, aar, Ein_En_Helse), by = c("aar")) %>% 
  mutate(andel = Eir_Er_Helse/Ein_En_Helse)
# LQjordbruk <- as_tibble(syssel_bos$Eir_Er_Jordbruk/nasjonalt_bosted$Ein_En_Jordbruk)
# LQundervisning <- as_tibble(syssel_bos$Eir_Er_Undervisning/nasjonalt_bosted$Ein_En_Undervisning)
# LQhelse <- as_tibble(syssel_bos$Eir_Er_Helse/nasjonalt_bosted$Ein_En_Helse)
```
